---
title: "Darwin_Data_Cleaning"
author: "Jessica Gephart"
date: "3/11/2019"
output: html_document
---

## Combine surveys

### Load packages and assign directory paths
```{r, echo=FALSE}
rm(list=ls())
library(easycsv)
library(tidyverse)

# Specify directory paths
in_dir <- "/nfs/jgephart-data/Darwin_data/1d Unzipped Monthly Survey Data" 
out_dir <- "/nfs/jgephart-data/Darwin_data/outputs"
```

### Create list of folders to load csv's
```{r, echo=FALSE}
folder_names <- list.files(in_dir,full.names=T) #this is the list of folder with RAW data information

#Screening to remove the directories that are not relevant
folder_names <- folder_names[grep(folder_names, pattern = "copy", invert = TRUE)]
folder_names <- folder_names[grep(folder_names, pattern = "MISC", invert = TRUE)]

folder_names <- unlist(lapply(folder_names,
                        function(x){list.files(path=x,full.names=T)}))

```

### Load files and bind by survey name
```{r, echo=FALSE}

for(i in 1:length(folder_names)){
  fread_folder(folder_names[i], data.table = FALSE)
}

file_names <- Filter(function(x) is.data.frame(get(x)), ls())

# Bind rows of single part surveys
# Fahasalamana
survey_df <- file_names[grep(file_names, pattern =  "Fahasalamana")] # FIXIT: Exclude "Fahasalamana isanbolana"

df <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}
Fahasalamana <- df
write.csv(Fahasalamana, file = file.path(out_dir, file = "Fahasalamana.csv"), row.names=FALSE)

# Fahasalamana isanbolana
survey_df <- file_names[grep(file_names, pattern =  "Fahasalamana isanbolana")]

df <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}
Fahasalamana_isanbolana <- df
write.csv(Fahasalamana_isanbolana, file = file.path(out_dir, "Fahasalamana_isanbolana.csv"), row.names=FALSE)

# Measure Sakafo
survey_df <- file_names[grep(file_names, pattern =  "Measure Sakafo")]

df <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}
Measure_Sakafo <- df
write.csv(Measure_Sakafo, file = file.path(out_dir, "Measure_Sakafo.csv"), row.names=FALSE)

# Vola isambolana
survey_df <- file_names[grep(file_names, pattern =  "Vola isambolana")]

df <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}
Vola_isambolana <- df
write.csv(Vola_isambolana, file = file.path(out_dir, "Vola_isambolana.csv"), row.names=FALSE)

# Bind columns, then rows of multi-part surveys
# FIXIT: Dates come in multiple formats; convert to standard format before joining
# Karazan-tsakafo
survey_df_all <- file_names[grep(file_names, pattern =  "Karazan-tsakafo")]
survey_df <- survey_df_all[grep(survey_df_all, pattern = "1 avy")]
df1 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df1 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

survey_df <- survey_df_all[grep(survey_df_all, pattern = "2 avy")]
df2 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df2 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

survey_df <- survey_df_all[grep(survey_df_all, pattern = "3 avy")]
df3 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df3 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

Karazan_tsakafo <- full_join(df1, df, by = c("Start Date", "Village", "Household"))
Karazan_tsakafo <- full_join(Karazan_tsakafo, df3, by = c("Start Date", "Village", "Household"))
write.csv(Karazan_tsakafo, file = file.path(out_dir, "Karazan_tsakafo.csv"), row.names=FALSE)

# Laoko
survey_df_all <- file_names[grep(file_names, pattern =  "Laoko")]
survey_df <- survey_df_all[grep(survey_df_all, pattern = "1 avy")]
df1 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df1 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

survey_df <- survey_df_all[grep(survey_df_all, pattern = "2 avy")]
df2 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df2 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

survey_df <- survey_df_all[grep(survey_df_all, pattern = "3 avy")]
df3 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df3 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

Laoko <- full_join(df1, df2, by = c("Start Date", "Village", "Household"))
Laoko <- full_join(Laoko, df3, by = c("Start Date", "Village", "Household"))
write.csv(Laoko, file = file.path(out_dir, "Laoko.csv"), row.names=FALSE)

# Mpanjono
survey_df_all <- file_names[grep(file_names, pattern =  "Mpanjono")]
survey_df <- survey_df_all[grep(survey_df_all, pattern = "1 avy")]
df1 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df1 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

survey_df <- survey_df_all[grep(survey_df_all, pattern = "2 avy")]
df2 <- plyr::rbind.fill(eval(parse(text = paste("`",survey_df[1],"`", sep=""))), eval(parse(text = paste("`",survey_df[2],"`", sep=""))))
for(i in 3:length(survey_df)){
  df2 <- plyr::rbind.fill(df, eval(parse(text = paste("`",survey_df[i],"`", sep=""))))
}

Mpanjono <- full_join(df1, df2, by = c("Start Date", "Village", "Household"))
write.csv(Mpanjono, file = file.path(out_dir, "Mpanjono.csv"), row.names=FALSE)

```

## Clean combined survey files

### Clean environment, reload packages, and load compiled data for cleaning
```{r, echo=FALSE}
rm(list=ls())
library(tidyverse)
library(easycsv)

dir <- "/nfs/jgephart-data/Darwin_data/outputs"
fread_folder(dir, data.table = FALSE)

```

## Cleaning steps
1. Translate column names to English (write out a file of the column names, add column to manually assign R-friendly English names, read back in to reassign column names)
2. Drop empty columns
3. Convert to correct data types (i.e. date, numeric, character, etc.). May have to remove text from numeric fields. 
4. Remove duplicate observations
5. Make data "tidy", where needed (e.g. with fish data) --> JAG has code for this
6. Check for:
* Number of observations in date-village combinations
* Outliers 

### Check date-village combinations
```{r, echo=FALSE}
colnames(Fahasalamana)[colnames(Fahasalamana )== "Code Village"] <- "Village"
colnames(Fahasalamana_isanbolana)[colnames(Fahasalamana_isanbolana )== "Code Village"] <- "Village"

colnames(Fahasalamana)[colnames(Fahasalamana )== "Start Date"] <- "Start.Date"
colnames(Fahasalamana_isanbolana)[colnames(Fahasalamana_isanbolana )== "Start Date"] <- "Start.Date"
colnames(Measure_Sakafo)[colnames(Measure_Sakafo )== "Start Date"] <- "Start.Date"
colnames(Vola_isambolana)[colnames(Vola_isambolana )== "Start Date"] <- "Start.Date"
colnames(Karazan_tsakafo)[colnames(Karazan_tsakafo )== "Start Date"] <- "Start.Date"
colnames(Laoko)[colnames(Laoko)== "Start Date"] <- "Start.Date"
colnames(Mpanjono)[colnames(Mpanjono)== "Start Date"] <- "Start.Date"

summary_village_date <- function(df){
  df$Start.Date <-as.Date(df$Start.Date, format = "%d/%m/%Y")
  df$YRMO <- as.factor(paste(year(df$Start.Date), month(df$Start.Date)))
  summary_table <- df %>% 
    group_by(YRMO, Village) %>%
    summarise()
  return(summary_table)
}

summary_table <- summary_village_date(Fahasalamana)
write.csv(summary_table, "summary_table_Fahasalamana.csv", row.names=FALSE)
summary_village_date(Fahasalamana_isanbolana)
write.csv(summary_table, "summary_table_Fahasalamana_isanbolana.csv", row.names=FALSE)
summary_village_date(Measure_Sakafo)
write.csv(summary_table, "summary_table_Measure_Sakafo.csv", row.names=FALSE)
summary_village_date(Vola_isambolana)
write.csv(summary_table, "summary_table_Vola_isambolana.csv", row.names=FALSE)
summary_village_date(Karazan_tsakafo)
write.csv(summary_table, "summary_table_Karazan_tsakafo.csv", row.names=FALSE)
summary_village_date(Laoko)
write.csv(summary_table, "summary_table_Laoko.csv", row.names=FALSE)
summary_village_date(Mpanjono)
write.csv(summary_table, "summary_table_Mpanjono.csv", row.names=FALSE)

```


### SECTION TITLE
```{r, echo=FALSE}

```



